### 2023-05-15 authorshipAndContributions.tex
new version

9 - Jane Goodall\\
Primatologist, Anthropologist\\
https://orcid.org/1111-2222-3333-2222 \custombullet~janegoodall@example.com\\
Contribution: Conceptualization, Writing – Original Draft Preparation, Writing – Review \& Editing

10 - Charles Darwin\\
Biologist, Naturalist\\
https://orcid.org/1111-2222-3333-3333 \custombullet~charlesdarwin@example.com\\
Contribution: Literature Review, Writing – Review \& Editing

11 - Barbara McClintock\\
Geneticist\\
https://orcid.org/1111-2222-3333-4444 \custombullet~barbaramcclintock@example.com\\
Contribution: Methodology, Data Analysis, Writing – Original Draft Preparation

>>>>

9 - Charles Darwin\\
Biologist, Naturalist\\
https://orcid.org/1111-2222-3333-3333 \custombullet~charlesdarwin@example.com\\
Contribution: Literature Review, Writing – Review \& Editing

10 - Barbara McClintock\\
Geneticist\\
https://orcid.org/1111-2222-3333-4444 \custombullet~barbaramcclintock@example.com\\
Contribution: Methodology, Data Analysis, Writing – Original Draft Preparation

### 2023-05-15 paper.tex
new version

\documentclass[english]{cenarticle}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
%
\portugueseTitle{O título em Português}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0001-0000-0000-0000]{Jane Goodall}{},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

\shortHeaderTitle{The title}
\shortHeaderAuthors{Carberry{\it~et~al.}}
%
\portugueseAbstract{
This research paper presents the results of an airborne experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity. The experiment utilized a specially designed aircraft equipped with sophisticated instrumentation and a computer system for data collection. By leveraging the concept of escape velocity, the team was able to gain altitude and enter stormy regions to capture relevant data. The study contributes to our understanding of the complex interactions between atmospheric phenomena and radioactivity.
}
%
\portugueseKeywords{aaa, bbb, ccc, ddd}
%
\englishAbstract{
This research paper presents the results of a groundbreaking experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity. The experiment introduces a unique instrument, the Espiralocirros-nimbodetector, which employs spores of Syagrus romanzoffiana (commonly known as the "coquinhos do mato") to measure air humidity. By utilizing this innovative device, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing intriguing insights into this fascinating phenomenon.
}
%
\englishKeywords{lightning, thunder, radioactivity, airborne experiment, escape velocity, storm}
%
%----------------------------------------------------------------------------------------
\begin{document}
  \coverpage

>>>>

\documentclass[english]{cenarticle}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
\usepackage{pgfplots}
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	PUBLISH INFO (not for authors)
%----------------------------------------------------------------------------------------
%
\issn{2179-460X}
%
\volume{44}
%
\eJournal{eXX}
%
\doi{https://doi.org/10.5902/2179460Xxxxxx}
%
\submitionDate{xx/xx/xx}
%
\approvalDate{xx/xx/xx}
%
\publishDate{xx/xx/xx}
%
\yearonfooter{xxxx}
%
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
%
\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

\shortHeaderTitle{The title}
\shortHeaderAuthors{Carberry{\it~et~al.}}
%
\portugueseAbstract{
Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade. 
Ao utilizar o Eletroplumbos-nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, proporcionando insights fascinantes sobre esse fenômeno intrigante. 
A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios, a frequência dos trovões e os níveis de radioatividade durante tempestades. Essas informações foram analisadas por meio de algoritmo Foobar, permitindo a identificação de correlações e padrões. 
Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como um grupo de controle para a comparação dos resultados. Essa abordagem meticulosa permitiu uma análise mais precisa dos efeitos específicos da interferência de raios e trovões na radioatividade. 
Os resultados obtidos revelam um aumento significativo nos níveis de radioatividade durante a ocorrência de raios e trovões, indicando uma clara influência desses fenômenos atmosféricos. 
Essa descoberta desafia as suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade. 
As implicações dessas descobertas são amplas e podem ter aplicações em diversos campos, incluindo a segurança nuclear, a proteção ambiental e até mesmo a previsão de tempestades e seus efeitos potenciais.
}
%
\portugueseKeywords{raio, trovão, radioatividade, experimento aéreo, velocidade de escape, tempestade}
%
\englishAbstract{
This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity. By utilizing the Electroplumbos-nimbodetector, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing fascinating insights into this intriguing phenomenon. 
The team collected accurate and quantitative data on the intensity of lightning, frequency of thunder, and levels of radioactivity during storms. This information was analyzed using the Foobar algorithm, allowing for the identification of correlations and patterns. 
Additionally, the team conducted comparative measurements in areas free from electrical activity, serving as a control group for result comparison. This meticulous approach enabled a more precise analysis of the specific effects of lightning and thunder interference on radioactivity. 
The obtained results reveal a significant increase in radioactivity levels during the occurrence of lightning and thunder, indicating a clear influence of these atmospheric phenomena. 
This discovery challenges previous assumptions and contributes to the advancement of knowledge regarding the effects of electrical activity on radioactivity. 
The implications of these findings are broad and can have applications in various fields, including nuclear safety, environmental protection, and even storm prediction and its potential effects.
}
%
\englishKeywords{lightning, thunder, radioactivity, airborne experiment, escape velocity, storm}
%
%----------------------------------------------------------------------------------------
\begin{document}
  \coverpage
